---
title: "Bio-Statistics"
subtitle: "\n"
author: "Xuchunhui（徐春晖）"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

class: center, middle, inverse

# Agenda 1: Disscusion

---
class:  middle


```{r echo=TRUE}

G1 <- c("徐文聪", "杜辉", "郭思坤", "陈心怡", "杜婧雯", "董宸", "姚瑶")
G2 <- c("胡粲", "吴晴歌", "陈玉宁", "肖辅", "徐盛", "吴玄慧", "杨颖超")
G3 <- c("关晓彤", "陶蕴华", "李颖", "王勇", "谢波", "魏华", "乌尼尔")
G4 <- c("肖静", "王引梅", "汪菲菲", "宗鑫", "左紫薇", "万启慧","吴琦")
G5 <- c("张景志", "姜瀛博", "谢永乐", "张朝霞", "汪丽华", "王丹洋", "黄鑫")
G6 <- c("李春", "肖伊人", "黄梦涵", "苏碧俏", "田世龙", "夏显霖")
G7 <- c("王俊杰", "肖礼万", "樊鲁玉", "王一洋", "武越" ,"韦彤")
```

---

class:  center, middle

# Homework Assign

```{r echo=FALSE}

(assign <- data.frame(homework = c(1:7), group = sample(1:7)))

```

---

class: center, middle, inverse

# Agenda 2: Report

---
class: center, middle

homowork-1

```{r echo=FALSE}
sample(G1,1)
```

---
class: center, middle

homowork-2

```{r echo=FALSE}
sample(G5,1)
```

---
class: center, middle

homowork-3

```{r echo=FALSE}
sample(G6,1)
```

---
class: center, middle

homowork-4

```{r echo=FALSE}
sample(G4,1)
```

---
class: center, middle

homowork-5

```{r echo=FALSE}
sample(G7,1)
```

---
class: center, middle

homowork-6

```{r echo=FALSE}
sample(G3,1)
```

---
class: center, middle

homowork-7

```{r echo=FALSE}
sample(G2,1)
```


---
class: inverse, center, middle

# Thanks for supporting
