---
title: "Bio-Statistics"
author:   "Xu Chunhui , E-mail: xuch@sibs.ac.cn"
date: "`r Sys.Date()`"
output: 
  ioslides_presentation:
    logo: "C:/Users/Chunhui Xu/Dropbox/Undergone/Statsitics/1st/cas.png"
    incremental: true
    smaller: true
    css: "C:/Users/Chunhui Xu/Dropbox/Undergone/Statsitics/1st/styles.css"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Agenda 1: Grouping

## Self-introduce 
<h1 style="color:blue;">This is a Blue Heading</h1>


<div class="red2">
**This text is red**
</div>

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

1. Simple lists are marked with bullets
1. Ordered lists begin with a number
1. You can even nest lists one inside another
    * Or mix their types
    * But do not go too far
    * Otherwise audience will be bored
1. Look, seven rows exactly!

## Slide with R Output

```{r cars, echo = TRUE}
shot <- c(6, 7, 7, 9, 6, 10, 5,8 ,9 ,6)
summary(shot)
mean(shot)
median(shot)
sd(shot)
var(shot)
sd(shot)/mean(shot)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

